An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-04-04 EconGrowthSeminar.Rnw
Clarified wording on some slides.

    \item{Statistically rigorous evaluation of energy types $Q$, $X$, and $U$}
    \pause
    \vspace{\baselineskip}

@@

\begin{frame}{Coordinates of Analysis} %----------------------------
  \begin{itemize}
    \item{Type of economy}
    \vspace{\baselineskip}
    \item{Type of energy}
    \vspace{\baselineskip}
    \item{Type of economic growth model}
  \end{itemize}
\end{frame}

@@

\begin{frame}{Type of Energy ($E$)} %----------------------------
  \begin{itemize}
    \item{Thermal energy ($Q$)}
    \vspace{\baselineskip}  
    \item{Exergy ($X$)}
    \vspace{\baselineskip}
    \item{Useful work ($U$)}
  \end{itemize}
  \vspace{\baselineskip}
  \pause
  \begin{center} Simplification: One type of energy ($Q$) for this presentation \end{center}
\end{frame}

@@

\begin{frame}{Economic Definitions} %----------------------------
  \begin{itemize}
    \item{Output ($Y$): total value (real 2005\$) of goods produced (GDP)}
    \vspace{\baselineskip}

@@

    \item{Labor ($L$): human work in an economy (persons or work hours)}
  \end{itemize}
\end{frame}

@@

    \item{Models (CD, or CES, without energy) could be \emph{included within} a system dynamics model that endogenizes price and cost share}
    \pause
    \item{System dynamics modeling}
  \end{itemize}
\end{frame}

>>>>

    \item{Statistically rigorous evaluation of energy quantifications $Q$, $X$, and $U$}
    \pause
    \vspace{\baselineskip}

@@

\begin{frame}{Coordinates of Analysis} %----------------------------
  \begin{itemize}
    \item{Type of economy}
    \vspace{\baselineskip}
    \item{Energy quantification}
    \vspace{\baselineskip}
    \item{Type of economic growth model}
  \end{itemize}
\end{frame}

@@

\begin{frame}{Energy ($E$) Quantification} %----------------------------
  \begin{itemize}
    \item{Thermal energy ($Q$)}
    \vspace{\baselineskip}  
    \item{Exergy ($X$)}
    \vspace{\baselineskip}
    \item{Useful work ($U$)}
  \end{itemize}
  \vspace{\baselineskip}
  \pause
  \begin{center} Simplification: Focus on $Q$ for this presentation \end{center}
\end{frame}

@@

\begin{frame}{Economic Definitions} %----------------------------
  \begin{itemize}
    \item{Output ($Y$): total value (real 2005\$/year) of goods produced (GDP)}
    \vspace{\baselineskip}

@@

    \item{Labor ($L$): human work in an economy (persons/year or work hours/year)}
  \end{itemize}
\end{frame}

@@

    \item{Models (CD, or CES, without energy) could be \emph{included within} a system dynamics model that endogenizes price and cost share}
  \end{itemize}
\end{frame}
